\documentclass[12pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath, amsthm}
\usepackage{epstopdf}
\usepackage{array}
\usepackage{url}
\usepackage{color}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcommand{\todo}[1]{{\color{red}$\blacksquare$~\textsf{[TODO: #1]}}}

\begin{document}

\noindent
\begin{tabular}{L{9.7cm} R{6.7cm}}
Astrophysical Radiation Processes: AS7005& Lab: 26.09.2022 \\
Evan O'Connor \& Yutong He & Due: 31.10.2022; on Athena\\
\end{tabular}\\

\vspace*{0.5cm}

\centerline{\Large \underline{Introduction to AS7005 Laboratory Exercise} }
\vspace*{0.5cm}

The purpose of this laboratory exercise is to solidify your
understanding of the fundamental radiation theory concept of
polarization, introduce you to some basic tools for radiation
transport, and get practice performing research, analysing results,
and writing scientifically.  These cover some of the learning outcomes
of the course, but also some of the learning outcomes of the Master's
program in general and is good preparation for the research project
later on in the degree program.  \newline

There is a prelab exercise (one of the standard weekly exercises) to
prep you for the content we will be looking at in the lab.  The lab
itself will be two parts.  The first will guide you through the
concepts of Thomson scattering, angular distributions, polarization,
Stokes parameters, and net polarization. Following this, the lab has
you perform Monto Carlo simulations of radiation transport with
photons from an aspherical supernovae in order to determine the net
polarization of the signal.  This will be the major work in the lab
session. The second part will be writing a paper-like lab report to
summarize the findings. Even though this research has been done before
(we'll see this below), when writing the report, please work under the
assumption you are doing this for the first time, typical for a
scientific paper. You can refer to the paper for the methods.  Please read
\mbox{\url{https://www.nature.com/articles/d41586-019-02918-5}} for
tips on writing scientifically.  \newline

For the paper please follow the outline below and pay attention to the
questions posed in the lab.  We suggest using overleaf
(\url{www.overleaf.com}), choose a new project with a template, choose
either ``Astronomy and Astrophysics'' or ``American Astronomical
Society''. Include an {\bf{Abstract}} summarizing the paper and the
findings.  An {\bf{Introduction}} where you give an general overview
of the astrophysical system we are modelling, and any other background
information needed for the paper. Include a summary of the layout of
the paper. Have a {\bf{Methods}} section where you discuss briefly the
theoretical model and methods (including a brief description of the
Monto Carlo transport).  Include key equations (e.g., among others,
the differential Thomson Scattering cross section, $d\sigma/d\Omega$)
and key derivations. Have a {\bf{Results}} section where you go through and
present the verification of the Monte Carlo simulations and the
results of the net polarization study. Please pay attention to the
specific questions asked in the lab and ensure you provide an answer
to them. End with a {\bf{Conclusions}} section where you discuss and
summarize the results. Wrap things up with assessing what you think
are the main limitations of the methods (including sources of error)
and possible improvements.
\newline

The lab write up is intended to be done independently. But you are
encouraged to have discussions with each other and the lab instructors
during the lab itself, but please come to your own conclusions,
present your own data in your own plots, answer the questions on your
own, and submit your own paper. An A will be given for a well written
paper that follows the above outline, shows an excellent understanding
of the methods and results, and uses the tools of the lab to go
further in the analysis or to provide insight beyond what what is
presented in the lab notebook. An acceptable lab report is required to
complete the course.  The lab component (the paper and the prelab
exercise) is 15\% of the total grade in the course. Please also save
the notebook and include in your submission a pdf copy of the jupyter
notebook you generated in the lab.  This will be especially useful
when you write up the lab, but also helps us with seeing your methods.

\newpage

{\Large{Background for the lab}}\\

Please read H\"oflich ``Asphericity effects in scattering dominated
photosphere'' A\&A 246 481 (1991).  The important parts are the
methods (Section 2) and results (Section 3), but not so much the
application to SN1987A (Section 4).  The purpose of the lab and topic
of your paper is reproduce a selection of the results in this paper.
Some methods and physical setups we use are different from H\"oflich
(1991), this is mainly for ease of implementation.  You are more than
welcome to enhance this work to includes these missing aspects, and
please discuss with us your thoughts and we can aide in your
endeavour and make sure you doesn't forget any key aspects.

As we saw in the the prelab exercise, Thomson scattering
dominated atmospheres polarize the light coming from different
regions.  If the atmosphere is asymmetric than this can lead to an
asymmetry polarization signal, and ultimately a net polarization from
the source as a whole.  In this lab, we will construct such asymmetric
atmospheres and follow the trajectory of individual photons being
emitted from the origin.  Since the scattering will be due to Thomson
scattering, the polarization state of the photons depends on the
history of the photon.  If we simulate enough photons we can determine
the polarization pattern and the net polarization.

The notebooks associated with this lab guide you through this whole
process.  Several key steps are missing, which will focus your
attention on the concepts relevant for this lab.  Please go through
the notebook slowly, read all the headers and comments and understand
what is happening. 



\end{document}
